Minicaml, a purely functional, didactical programming language with an interactive REPL. WORK IN PROGRESS DRAFT

### 2019-12-25 paper/paper.tex
fixed wrong opam file

\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{floatflt}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{amsthm}
\usepackage{subfig}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{titling}
\usepackage{minibox}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage[strict]{changepage}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{matrix}
\pgfplotsset{width=11cm,compat=1.9}
\usepgfplotslibrary{external}
\tikzexternalize

@@

\title{Minicaml, a purely functional, didactical programming language with an
interactive REPL. WORK IN PROGRESS DRAFT}
\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
\begin{document}
\begin{titlingpage}
\maketitle

\begin{abstract}
\textbf{minicaml} is a small, purely functional interpreted programming language
with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
Francesca Levi's minicaml, an evaluation example to show students attending the
Programming 2 course at the University of Pisa how interpreters work. It is an
interpreted language featuring a Caml-like syntax, static (lexical scoping),
interchangeable eager and lazy evaluation and a didactical REPL that
shows each AST expression and each evaluation step.
\end{abstract}
\end{titlingpage}

@@

\section{Lexer}

@@

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework. Code
coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
page containing the coverage percentage when unit tests are run by the dune
build system. After each commit is pushed to the remote source repository on
Github, the package is built and tests are run by the Travis Continuos
Integration system.

\section{Thanks}
Thanks to Antonio DeLucreziis for helping me implement lazy evaluation.

\end{document}

>>>>

\documentclass[a4paper, 11pt]{article}

%% Language and font encodings. This says how to do hyphenation on end of lines.
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{xcolor}
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.5pt}
%\usepackage{aas_macros}

%% Sets page size and margins. You can edit this to your liking
\usepackage[top=1.3cm, bottom=2.0cm, outer=2.5cm, inner=2.5cm, heightrounded,
marginparwidth=1cm, marginparsep=0.4cm, margin=1.5cm]{geometry}

%% Useful packages
\usepackage{graphicx} %allows you to use jpg or png images. PDF is still recommended
\usepackage[colorlinks=False]{hyperref} % add links inside PDF files
\usepackage{amsmath}  % Math fonts
\usepackage{amsfonts} %
\usepackage{amssymb}  %

@@

%% Citation package
\usepackage[authoryear]{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}

\title{Minicaml, a purely functional, didactical programming language with an
interactive REPL. WORK IN PROGRESS DRAFT}
\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}

\begin{document}
\maketitle

\begin{abstract}
\textbf{minicaml} is a small, purely functional interpreted programming language
with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
Francesca Levi's minicaml, an evaluation example to show students attending the
Programming 2 course at the University of Pisa how interpreters work. It is an
interpreted language featuring a Caml-like syntax, static (lexical scoping),
interchangeable eager and lazy evaluation and a didactical REPL that
shows each AST expression and each evaluation step.
\end{abstract}

@@

\begin{multicols}{2}
\section{Lexer}

@@

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework. Code
coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
page containing the coverage percentage when unit tests are run by the dune
build system. After each commit is pushed to the remote version control repository on
Github, the package is built and tests are run thanks to the Travis Continuos
Integration system.

\section{Thanks to}

\begin{itemize}
	\item Prof. Gian-Luigi Ferrari for teaching us how to project and develop
	interpreters in OCaml
	\item Antonio DeLucreziis for helping me implement lazy evaluation.
	\item Prof. Alessandro Berarducci for helping me study lambda calculus in deep.
\end{itemize}

\end{multicols}
\end{document}
